---
title: "Analysis of video surveys from CANDOUR project. Version using odds ratios."
date: "`r format(Sys.time(), '%d %B %Y')`"
output: pdf_document
header-includes:
 - \usepackage{rotating}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, dpi=500)
library(tidyverse)
#library(stargazer)
#library(kableExtra)
#library(viridis)
#library(viridisLite)
library(hrbrthemes)
#library(readxl)
library(estimatr)
library(Matching)
library(nnet)
library(dplyr)
options(dplyr.summarise.inform=FALSE) # remove annoying warning
library(conflicted)
#library(plyr)
library(dplyr) #
library(flextable)
library(binom) # for confidence intervals
library(xtable)
#library(INLA) # For Bayes models
#library(R2WinBUGS) # For Bayes models
#bugs_loc = "c:/Program Files/WinBUGS14"
source('99_functions.R')

select <- dplyr::select
conflict_prefer("filter", "dplyr")
conflict_prefer("mutate", "dplyr")
conflict_prefer("rename", "dplyr")
conflict_prefer("summarize", "dplyr")
conflict_prefer("recode", "dplyr")

# get the data from 0_read_data.R
load('data/analysis_ready.RData')
```


## Baseline comparison table

The total number of responses is `r nrow(pretest_final)`.

### a) categorical variables, cells show counts and percents

```{r}
cat_table = select(pretest_final, Treatment2, pool, gender, Education, Race) %>%
  pivot_longer(cols=c('pool','gender','Education','Race')) %>%
  mutate(
    value = ifelse(is.na(value), 'Missing', value)) %>% # flag missing
  group_by(Treatment2, name, value) %>%
  tally() %>%
  group_by(Treatment2, name) %>%
  mutate(percent = round(100*prop.table(n)), # calculate percent
         cell = paste(n, ' (', percent, ')', sep='')) %>%
  ungroup() %>%
  select(Treatment2, name, value, cell) %>%
  pivot_wider(names_from=Treatment2, values_from=cell) %>%
  dplyr::arrange(name, value)
ftab = flextable(cat_table) %>%
  theme_box() %>%
  fontsize(size=10, part='all') %>%
  autofit() %>%
  merge_v(j=1) 
ftab
```

### b) Continuous variables, cells show median and inter-quartile range

```{r}
cont_table = select(pretest_final, Treatment2, Trumppercent, age) %>%
  mutate(Trumppercent = Trumppercent*100) %>% # from proportion to percent
  pivot_longer(cols=c('Trumppercent','age')) %>%
  group_by(Treatment2, name) %>%
  dplyr::summarise(N = n(), 
                   missing = sum(is.na(value)), 
                   median = median(value, na.rm=TRUE),
                   lower = quantile(value, na.rm=TRUE, 0.25),
                   upper = quantile(value, na.rm=TRUE, 0.75),
                   median = round(median),
                   lower = round(lower),
                   upper = round(upper)) %>%
  ungroup() %>%
  mutate(cell = paste(median, ' (', lower, ' to ', upper, ')', sep='')) %>%
  select(Treatment2, name, cell) %>%
  pivot_wider(names_from=Treatment2, values_from=cell)
ftab = flextable(cont_table) %>%
  theme_box() %>%
  autofit()
ftab
```

### Bayesian logistic regression

Here we use a Bayesian logistic regression model with a random intercept for each state and a random intercept for the three sampling pools (Facebook, CloudResearch, Lucid). 

```{r}
# set up data for bayes model:
source('1_bayes_model.R')
# get results from lyra
load("//hpc-fs/barnetta/vaccine/jags_results_full.RData")
dic3 = data.frame(pD = pD, DIC = DIC)
# make estimated probabilities for later plot
p1 = data.frame(row=1, chain=1, est=output$alpha[1,,1]) %>% mutate(x=1:n())
p2 = data.frame(row=2, chain=1, est=output$alpha[1,,1] + output$alpha[2,,1]) %>% mutate(x=1:n())
p3 = data.frame(row=3, chain=1, est=output$alpha[1,,1] + output$alpha[3,,1]) %>% mutate(x=1:n())
p4 = data.frame(row=1, chain=2, est=output$alpha[1,,2]) %>% mutate(x=1:n())
p5 = data.frame(row=2, chain=2, est=output$alpha[1,,2] + output$alpha[2,,2]) %>% mutate(x=1:n())
p6 = data.frame(row=3, chain=2, est=output$alpha[1,,2] + output$alpha[3,,2]) %>% mutate(x=1:n())
chains = bind_rows(p1, p2, p3, p4, p5, p6) %>%
  mutate(p = exp(est)/(1+exp(est)))

# absolute difference in probabilities
abs = select(chains, -est) %>%
  pivot_wider(values_from = p, names_from = row) %>%
  mutate(diff1 = `2` - `1`, # cash minus CDC
         diff2 = `3` - `1`) %>% # lottery minus CDC
  summarise(m1 = mean(diff1), l1 = quantile(diff1, 0.025), u1 = quantile(diff1, 0.975),
            m2 = mean(diff2), l2 = quantile(diff2, 0.025), u2 = quantile(diff2, 0.975))
```

```{r}
# table of estimates
table3 = filter(alpha, chain==99)
table3$Variable = colnames(X)
table = select(table3, 'Variable', 'mean', 'lower', 'upper', 'pvalue') %>%
  filter(!str_detect(Variable, 'Intercept')) %>% # remove intercept
  mutate(
     Variable = nice_rename(Variable),
     OR = roundz(exp(mean), 2),
    lower = roundz(exp(lower), 2),
    upper = roundz(exp(upper), 2),
    pvalue = format.pval(pvalue, eps=0.001, digits=2),
    CI = paste(lower, ' to ', upper, sep='')) %>%
  select(Variable, OR, CI, pvalue)
ftab = flextable(table) %>%
  theme_box() %>%
  autofit()
ftab
# for latex:
print(xtable(table, type = "latex"), file = "model3.tex", include.rownames=FALSE)
```

The table shows the odds ratios, 95% credible intervals, and a Bayesian p-values which estimate the probability that the odds ratio is not equal to 1. 

The absolute difference in probability between the cash voucher and CDC is `r roundz(abs$m1, 2)` with a 95% credible interval from `r roundz(abs$l1, 2)` to `r roundz(abs$u1, 2)`. The absolute difference in probability between the lottery and CDC is `r roundz(abs$m2, 2)` with a 95% credible interval from `r roundz(abs$l2, 2)` to `r roundz(abs$u2, 2)`.

### Plot of random state effects

The plot shows the mean and 95% credible interval.

```{r, fig.height=8}
to_plot = filter(lambda, chain==99)
rplot = ggplot(to_plot, aes(x=row, y=exp(mean), ymin=exp(lower), ymax=exp(upper)))+
  geom_hline(yintercept=1, lty=2)+
  geom_point()+
  geom_errorbar(width=0)+
  scale_x_continuous(breaks=1:50, expand=c(0.01,0.01))+ #
  xlab('')+
  ylab('Odds ratio')+
  theme_bw()+
  theme(panel.grid.minor = element_blank())+
  coord_flip()
rplot
```

The differences between states were small.

### Plot of random pool effects

```{r, fig.height=3}
to_plot = filter(gamma, chain==99)
rplot = ggplot(to_plot, aes(x=row, y=exp(mean), ymin=exp(lower), ymax=exp(upper)))+
  geom_hline(yintercept=1, lty=2)+
  geom_point()+
  geom_errorbar(width=0)+
  scale_x_continuous(breaks=1:3, labels=c('CloudResearch','Facebook','Lucid'))+
  xlab('')+
  ylab('Odds ratio')+
  theme_bw()+
  theme(panel.grid.minor = element_blank())+
  coord_flip()
rplot
```

Facebook users had a higher click-through probability whereas Lucid users had a lower click-through probability.

## Bayesian logistic regression models

The table below shows the results for unadjusted (model 1) and adjusted estimates (models 2 and 3).

```{r}
## unadjusted
source('1_bayes_model_unadjusted.R')
# get results from lyra
load("//hpc-fs/barnetta/vaccine/jags_results_unadjusted.RData")
table1 = filter(alpha, chain==99)
table1$Variable = colnames(X)
dic1 = data.frame(pD = pD, DIC = DIC)

## adjusted
source('1_bayes_model_adjusted.R')
# get results from lyra
load("//hpc-fs/barnetta/vaccine/jags_results_adjusted.RData")
table2 = filter(alpha, chain==99)
table2$Variable = colnames(X)
dic2 = data.frame(pD = pD, DIC = DIC)
```

```{r}
# table of estimates
table = bind_rows(table1, table2, table3, .id='model') %>%
  filter(chain == 99) %>%
  select('model','Variable', 'mean', 'lower', 'upper') %>%
  filter(!str_detect(Variable, 'Intercept')) %>% # remove intercept
  mutate(
    Variable = nice_rename(Variable),
    OR = roundz(exp(mean), 2),
    lower = roundz(exp(lower), 2),
    upper = roundz(exp(upper), 2),
    #pvalue = format.pval(pvalue, eps=0.001, digits=2),
    CI = paste(lower, ' to ', upper, sep=''),
    cell = paste(OR, ' (', CI, ')', sep='')) %>%
  select(model, Variable, cell) %>%
  pivot_wider(names_from=model, values_from=cell)
ftab = flextable(table) %>%
  theme_box() %>%
  autofit()
ftab
# for latex:
print(xtable(table, type = "latex"), file = "multiple_models.tex", include.rownames=FALSE)
```

Model 1 = Treatment only.

Model 2 = Treatment plus predictors.

Model 3 = Treatment plus predictors and random effects for state and pool.

The table below compares the model fit using the DIC.

```{r}
# table of estimates
table = bind_rows(dic1, dic2, dic3, .id='model')
ftab = flextable(table) %>%
  colformat_num(j=2, digits=1) %>%
  colformat_num(j=3, digits=0) %>%
  theme_box() %>%
  autofit()
ftab
```

Model 3 has the largest effective number of parameters (pD), and by far the best model fit (smallest DIC).

## Plot of results by treatment group

```{r}
## use fully adjusted model
to_plot = filter(table3, chain==99, row > 1) %>%  # not intercept
  mutate(mean = exp(mean),
         lower = exp(lower),
         upper = exp(upper),
         col = 1 + as.numeric(row > 3), # for colouring lines
         col = factor(col)) %>%
  select(row, Variable, col, mean, lower, upper) 
#
xlabels = nice_rename(to_plot$Variable) # labels for x-axis
#
plot = ggplot(data=to_plot, aes(x=row, y=mean, ymin=lower, ymax=upper, col=col))+
  xlab('')+
  ylab('Odds ratio')+
  scale_x_reverse(breaks=2:10, labels=xlabels)+
  geom_hline(yintercept=1, lty=2, size=1.05)+
  scale_color_manual(NULL, values=c('dodgerblue','darkseagreen3'))+
  geom_point(size=4)+
  geom_errorbar(width=0, size=1.04)+
  coord_flip()+
  theme_bw()+
  theme(legend.position='none',
        panel.grid.minor = element_blank())
plot
jpeg('figures/bayes_estimates_OR.jpg', width=4, height=5, units='in', res=600)
print(plot)
invisible(dev.off())
png('figures/logistic_OR.png', width=4.5, height=5.5, units='in', res=600)
print(plot)
invisible(dev.off())
```

The "CDC Health Information" is the reference group.

## Treatment interactions

### a) Gender interaction

The table below shows the main effects and interaction for the gender by treatment interaction. The other variables (e.g., age) were also adjusted for.

```{r}
## 
source('1_bayes_model_gender_interaction.R')
# get results from lyra
load("//hpc-fs/barnetta/vaccine/jags_results_male.RData")
table = filter(alpha, chain==99) 
table$Variable = colnames(X)
#
table = filter(table, !str_detect(Variable, 'Intercept')) %>% # remove intercept
  mutate(
    Variable = nice_rename(Variable),
    Variable = ifelse(Variable=='int1', 'Male x cash voucher', Variable),
    Variable = ifelse(Variable=='int2', 'Male x lottery', Variable),
    OR = roundz(exp(mean), 2),
    lower = roundz(exp(lower), 2),
    upper = roundz(exp(upper), 2),
    pvalue = format.pval(pvalue, eps=0.001, digits=2),
    CI = paste(lower, ' to ', upper, sep='')) %>%
  select(Variable, OR, CI, pvalue)
ftab = flextable(table) %>%
  theme_box() %>%
  autofit()
ftab
# for latex:
print(xtable(table, type = "latex"), file = "table_gender_interaction.tex", include.rownames=FALSE)
```

The reference gender for race is "non-male".

```{r, include=FALSE}
## construct probabilities by gender
#formula = clicked ~ trt2_c + trt2_l + male + int1 + int2 + ...
#int1 =trt2_c*male, # make interactions
#int2 =trt2_l*male
# make table of what chains to use
design = read.table(header=TRUE, sep=',', stringsAsFactors = FALSE, text='
Gender,Treatment,x1,x2,x3,x4,x5,x6
Female,control,1,0,0,0,0,0
Male,control,1,0,0,1,0,0
Female,cash,1,1,0,0,0,0
Male,cash,1,1,0,1,1,0
Female,lottery,1,0,1,0,0,0
Male,lottery,1,0,1,1,0,1')
ests_gender = make_ests(design = design, chains = output$alpha, type='OR')
#
```

### b) Race interaction

The table below shows the main effects and interaction for the race by treatment interaction. The other variables (e.g., age) were also adjusted for.

```{r}
## 
source('1_bayes_model_race_interaction.R')
# get results from lyra
load("//hpc-fs/barnetta/vaccine/jags_results_race.RData")
table = filter(alpha, chain==99) 
table$Variable = colnames(X)
#
table = filter(table, !str_detect(Variable, 'Intercept')) %>% # remove intercept
  mutate(
    Variable = nice_rename(Variable),
    Variable = ifelse(Variable=='int1', 'Other race x cash voucher', Variable),
    Variable = ifelse(Variable=='int2', 'Other race x lottery', Variable),
    Variable = ifelse(Variable=='int3', 'Black race x cash voucher', Variable),
    Variable = ifelse(Variable=='int4', 'Black race x lottery', Variable),
    OR = roundz(exp(mean), 2),
    lower = roundz(exp(lower), 2),
    upper = roundz(exp(upper), 2),
    pvalue = format.pval(pvalue, eps=0.001, digits=2),
    CI = paste(lower, ' to ', upper, sep='')) %>%
  select(Variable, OR, CI, pvalue)
ftab = flextable(table) %>%
  theme_box() %>%
  autofit()
ftab
# for latex:
print(xtable(table, type = "latex"), file = "table_race_interaction.tex", include.rownames=FALSE)
```

The reference group for race is "white".

```{r, include=FALSE}
## construct probabilities by race
# formula = clicked ~ trt2_c + trt2_l + race1 + race2 + int1 + int2 + int3 + int4 +
# int1 = trt2_c*race1, # make interactions
#                       int2 = trt2_l*race1,
#                       int3 = trt2_c*race2,
#                       int4 = trt2_l*race2...
# make table of what chains to use
design = read.table(header=TRUE, sep=',', stringsAsFactors = FALSE, text='
Race,Treatment,x1,x2,x3,x4,x5,x6,x7,x8,x9
White,control,1,0,0,0,0,0,0,0,0
Other,control,1,0,0,1,0,0,0,0,0
Black,control,1,0,0,0,1,0,0,0,0
White,cash,1,1,0,0,0,0,0,0,0
Other,cash,1,1,0,1,0,1,0,0,0
Black,cash,1,1,0,0,1,0,0,1,0
White,lottery,1,0,1,0,0,0,0,0,0
Other,lottery,1,0,1,1,0,0,1,0,0
Black,lottery,1,0,1,0,1,0,0,0,1')
ests_race = make_ests(design = design, chains = output$alpha, type='OR')
#
```

### c) Education interaction

The table below shows the main effects and interaction for the education by treatment interaction. The other variables (e.g., age) were also adjusted for.

```{r}
## 
source('1_bayes_model_education_interaction.R')
# get results from lyra
load("//hpc-fs/barnetta/vaccine/jags_results_education.RData")
table = filter(alpha, chain==99) 
table$Variable = colnames(X)
#
table = filter(table, !str_detect(Variable, 'Intercept')) %>% # remove intercept
  mutate(
    Variable = nice_rename(Variable),
    Variable = ifelse(Variable=='int1', 'Medium education x cash voucher', Variable),
    Variable = ifelse(Variable=='int2', 'Medium education x lottery', Variable),
    Variable = ifelse(Variable=='int3', 'High education x cash voucher', Variable),
    Variable = ifelse(Variable=='int4', 'High education x lottery', Variable),
    OR = roundz(exp(mean), 2),
    lower = roundz(exp(lower), 2),
    upper = roundz(exp(upper), 2),
    pvalue = format.pval(pvalue, eps=0.001, digits=2),
    CI = paste(lower, ' to ', upper, sep='')) %>%
  select(Variable, OR, CI, pvalue)
ftab = flextable(table) %>%
  theme_box() %>%
  autofit()
ftab
# for latex:
print(xtable(table, type = "latex"), file = "table_education_interaction.tex", include.rownames=FALSE)
```

The reference group for education is "low".

```{r, include=FALSE}
## construct probabilities by education
# formula = clicked ~ trt2_c + trt2_l + edu1 + edu2 + int1 + int2 + int3 + int4 +
# int1 = trt2_c*edu1, # make interactions
#                       int2 = trt2_l*edu1,
#                       int3 = trt2_c*edu2,
#                       int4 = trt2_l*edu2...
# make table of what chains to use
design = read.table(header=TRUE, sep=',', stringsAsFactors = FALSE, text='
Education,Treatment,x1,x2,x3,x4,x5,x6,x7,x8,x9
Low,control,1,0,0,0,0,0,0,0,0
Medium,control,1,0,0,1,0,0,0,0,0
High,control,1,0,0,0,1,0,0,0,0
Low,cash,1,1,0,0,0,0,0,0,0
Medium,cash,1,1,0,1,0,1,0,0,0
High,cash,1,1,0,0,1,0,0,1,0
Low,lottery,1,0,1,0,0,0,0,0,0
Medium,lottery,1,0,1,1,0,0,1,0,0
High,lottery,1,0,1,0,1,0,0,0,1')
ests_education = make_ests(design = design, chains = output$alpha, type='OR')
#
```

### d) Percent Trump vote

The table below shows the main effects and interaction for the trump vote by treatment interaction. The other variables (e.g., age) were also adjusted for.

```{r}
## 
source('1_bayes_model_trump_interaction.R')
# get results from lyra
load("//hpc-fs/barnetta/vaccine/jags_results_trump.RData")
table = filter(alpha, chain==99) 
table$Variable = colnames(X)
#
table = filter(table, !str_detect(Variable, 'Intercept')) %>% # remove intercept
  mutate(
    Variable = nice_rename(Variable),
    Variable = ifelse(Variable=='int1', 'Trump x cash voucher', Variable),
    Variable = ifelse(Variable=='int2', 'Trump x lottery', Variable),
    OR = roundz(exp(mean), 2),
    lower = roundz(exp(lower), 2),
    upper = roundz(exp(upper), 2),
    pvalue = format.pval(pvalue, eps=0.001, digits=2),
    CI = paste(lower, ' to ', upper, sep='')) %>%
  select(Variable, OR, CI, pvalue)
ftab = flextable(table) %>%
  theme_box() %>%
  autofit()
ftab
# for latex:
print(xtable(table, type = "latex"), file = "table_trump_interaction.tex", include.rownames=FALSE)
```

```{r, include=FALSE}
## construct probabilities by trump vote
formula = clicked ~ trt2_c + trt2_l + male + int1 + int2 + age_c + Race + Education + trumppercent 
#int1 =trt2_c*trump, # make interactions
#int2 =trt2_l*trump
# make table of what chains to use
design = read.table(header=TRUE, sep=',', stringsAsFactors = FALSE, text='
Trump,Treatment,x1,x2,x3,x4,x5,x6,x7,x8,x9,x10
Average,control,1,0,0,0,0,0,0,0,0,0
Plus 10%,control,1,0,0,0,0,0,0,0,0,1
Average,cash,1,1,0,0,0,0,0,0,0,0
Plus 10%,cash,1,1,0,0,1,0,0,0,0,1
Average,lottery,1,0,1,0,0,0,0,0,0,0
Plus 10%,lottery,1,0,1,0,0,1,0,0,0,1')
ests_trump = make_ests(design = design, chains = output$alpha, type='OR')
#
```


## Plot of interaction effects

```{r}
# combine estimates
combined = bind_rows(ests_gender, ests_race, ests_education, ests_trump, .id='variable') %>%
  mutate(
    trt_num = case_when(
      Treatment == 'cash' ~ 2,
      Treatment == 'lottery' ~ 3
  ),
  Variable = case_when(
      variable == 1 ~ "Gender",
      variable == 2 ~ "Race",
      variable == 3 ~ "Education",
      variable == 4 ~ "State Trump vote"
  ),
  label = case_when(
    variable == 1 ~ Gender,
    variable == 2 ~ Race,
    variable == 3 ~ Education,
    variable == 4 ~ Trump
  )) %>%
  mutate(labelf = factor(label, levels=c('Female','Male','White','Other','Black','Low','Medium','High','Average','Plus 10%'))) # for axis ordering
cplot = ggplot(data=combined, aes(y=labelf, x=mean, xmin=lower, xmax=upper, col=factor(trt_num))) +
  geom_vline(lty=2, size=1.05, col='grey', xintercept=1)+
  geom_point(size=3, position=position_dodge(width=0.25))+
  geom_errorbarh(size=1.02, height=0, position=position_dodge(width=0.25))+
  scale_color_manual('Treatment', values=c('dark green','dodgerblue'), labels=c('Cash Voucher','Lottery'))+
  xlab('Odds ratio')+
  ylab('')+
  facet_wrap(~Variable, scales='free_y')+
  theme_bw()+
  theme(legend.position='top',
        panel.grid.minor = element_blank())
cplot
jpeg('figures/bayes_interactions_OR.jpg', width=5.5, height=5, units='in', res=600)
print(cplot)
invisible(dev.off())
png('figures/interactions_OR_relative.png', width=5.5, height=5, units='in', res=600)
print(cplot)
invisible(dev.off())
```

#### Table of odds ratio estimates from above plot

The table below gives the odds ratios and 95% credible intervals shown in the previous plot.


```{r}
to_table = select(combined, Variable, Treatment, labelf, mean, lower, upper) %>%
  rename('category' = 'labelf')
ftab = flextable(to_table) %>%
  merge_v(j=1:2) %>%
  theme_box() %>%
  colformat_num(j=4:6, digits=2) %>%
  autofit()
ftab
```

## Plot of probability ratios

```{r}
cplot = ggplot(data=combined, aes(y=labelf, x=prmean, xmin=prlower, xmax=prupper, col=factor(trt_num))) +
  geom_vline(lty=2, size=1.05, col='grey', xintercept=1)+
  geom_point(size=3, position=position_dodge(width=0.25))+
  geom_errorbarh(size=1.02, height=0, position=position_dodge(width=0.25))+
  scale_color_manual('Treatment', values=c('dark green','dodgerblue'), labels=c('Cash Voucher','Lottery'))+
  xlab('Probability ratio')+
  ylab('')+
  facet_wrap(~Variable, scales='free_y')+
  theme_bw()+
  theme(legend.position='top',
        panel.grid.minor = element_blank())
cplot
jpeg('figures/bayes_interactions_PR.jpg', width=5.5, height=4, units='in', res=600)
print(cplot)
invisible(dev.off())
png('figures/interactions_PR_fixed.png', width=5.5, height=4, units='in', res=600)
print(cplot)
invisible(dev.off())
```

## For supplement: check of Bayesian model convergence

```{r}
#
load("//hpc-fs/barnetta/vaccine/jags_results_full.RData")
# prepare data for plot
p1 = data.frame(row=1, chain=1, est=output$alpha[1,,1]) %>% mutate(x=1:n())
p2 = data.frame(row=2, chain=1, est=output$alpha[2,,1]) %>% mutate(x=1:n())
p3 = data.frame(row=3, chain=1, est=output$alpha[3,,1]) %>% mutate(x=1:n())
p4 = data.frame(row=1, chain=2, est=output$alpha[1,,2]) %>% mutate(x=1:n())
p5 = data.frame(row=2, chain=2, est=output$alpha[2,,2]) %>% mutate(x=1:n())
p6 = data.frame(row=3, chain=2, est=output$alpha[3,,2]) %>% mutate(x=1:n())
chains = bind_rows(p1, p2, p3, p4, p5, p6)  %>% 
  mutate(facet = case_when(
    row ==1 ~ "Intercept",
    row ==2 ~ "Treatment 1",
    row ==3 ~ "Treatment 2"
  ))
#
cplot = ggplot(data=chains, aes(x=x, y=est, col=factor(chain)))+
  scale_color_manual('Chain', values=c('skyblue','orange'))+
  geom_line()+
  theme_bw()+
  xlab('')+
  ylab('logit')+
  facet_wrap(~facet)
cplot
```

The plots show 5,000 samples that were thinned by 5. The burn-in was 5,000. Convergence and mixing look good. These are the estimates from model 3.